Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-15 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4540 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

Overall we find the results for interposer-based FPGAs to be very positive. While an interposer can only provide a fraction of the signal count between dice that one would have across cutline within a die, the system still has excellent routability and behaves similarly to a monolithic FPGA so long as the interposer signal count is not pushed to very low values; approximately 15\% of the within-die routing in our experiments. We have also found that modifications to the FPGA CAD flow and routing architecture to exploit interposer-based FPGAs have been very productive. As this is a new area we believe more routability and timing enhancements are likely with further research, and this would further enhance the utility of interposer-based FPGAs.

>>>>

Overall we find the results for interposer-based FPGAs to be very positive. While an interposer can only provide a fraction of the signal count between dice that one would have across cutline within a die, the system still has excellent routability and behaves similarly to a monolithic FPGA so long as the interposer signal count is not pushed to very low values; below 20\% of the within-die routing in our experiments. We have also found that modifications to the FPGA CAD flow and routing architecture to exploit interposer-based FPGAs have been very productive. As this is a new area we believe more routability and timing enhancements are likely with further research, and this would further enhance the utility of interposer-based FPGAs.
